Structured Genealogy Processes

### 2022-01-05 ms.Rnw
housekeeping work for the SGP paper
constellation diagram

@@

\bibliographystyle{preprint}
\bibliography{phylopomp}

>>>>

\begin{figure}
  \resizebox{0.6\linewidth}{!}{
    \begin{tikzpicture}[scale=1.8]
      \usetikzlibrary{arrows}
      \tikzstyle{coordinate}=[inner sep=0pt,outer sep=0pt]
      \tikzstyle{det}=[color=black, thick, >=stealth]
      \tikzstyle{stoch}=[color=black, dashed, thick, >=stealth]
      \node (O) at (0,0) {$\Master_t$};
      \node (X) at (180:2) {$\X_t$};
      \node (H) at (210:2) {$\Hist_t$};
      \node (I) at (240:2) {$\Inv_t$};
      \node (G) at (270:2) {$\Gen_t$};
      \node (P) at (300:2) {$\Prune_t$};
      \node (V) at (330:2) {$\Vis_t$};
      \node (W) at (360:2) {$\Wch_i$};
      \draw [det,->] (O) -- (X);
      \draw [det,->] (O) -- (H);
      \draw [det,->] (H) -- (X);
      \draw [det,->] (O) -- (I);
      \draw [det,->] (O) -- (G);
      \draw [det,->] (O) -- (P);
      \draw [det,->] (O) -- (V);
      \draw [det,->] (O) -- (W);
      \draw [det,->] (V) -- (W);
      \draw [det,->] (G) -- (I) node[midway,below,sloped] {$\mathrm{ext}$};
      \draw [det,->] (G) -- (P) node[midway,below,sloped] {$\mathrm{prune}$};
      \draw [det,->] (P) -- (V) node[midway,below,sloped] {$\mathrm{obs}$};
      \draw [stoch,->] (H) -- (I);
      \draw [stoch,->] (H) -- (G);
      \draw [stoch,->] (H) -- (V);
      \draw [stoch,->] (H) -- (W);
    \end{tikzpicture}
  }
  \caption{
    \label{fig:constellation}
    Relations among the various Markov processes discussed in the paper.
    Deterministic maps are indicated with solid arrows;
    random maps are shown as dashed arrows.
    All the maps shown commute.
    $\X_t$ is the \emph{population process}, a model of the dynamics of some system, which we take as a starting point.
    $\Hist_t$ is the \emph{history process}, which records the full history of $\X_t$.
    $\Inv_t$ is the \emph{inventory process}: at each time $t$, $\Inv_t$ is an inventory of all extant individuals in the population, each of which has a globally unique name.
    $\Gen_t$ is the \emph{genealogy process}, which captures the precise genealogical relationships among all individuals in $\Inv_t$, as well as among any samples that have been taken from the population.
    $\Vis_t$ is the \emph{visible genealogy process}, which is $\Gen_t$ pruned so that only relationships among samples remain.
    Finally $\Wch_i$ is the \emph{embedded chain of the visible genealogy process}, which is $\Vis_{s_i}$, $s_i$ being the time of the $i$-th sample.
    All of these processes can be obtained via deterministic procedures applied to the \emph{master process} $\Master_t$, as described in the text.
  }
\end{figure}

@@

\bibliographystyle{../preprint}
\bibliography{phylopomp}
